### 2019-04-11 Thesis/games.tex
old.

At type $\Var$, we have terms that call the read and write `methods' to dereference the variable or to assign a new value to it.
\begin{mathpar}
  \inferrule*{\Gamma\ts V \from \Var}{\Gamma \ts \oc V \from \nat}
  \and
  \inferrule*{\Gamma\ts V \from \Var \\ \Gamma \ts E \from \nat}{\Gamma \ts V\gets E \from \com}
\end{mathpar}

@@

\begin{proposition}[\cite{SamsonGuyIAActive}]
  Suppose that $\Gamma,s\ts M\converges c,s'$.  
  Then
  \[
    \deno s;\cell^\Gamma;\deno{\Gamma\ts M} = \deno{s'};\cell^\Gamma;\deno{\Gamma\ts c}\,.
    \]
\end{proposition}
\begin{proof}
  Lemma \ref{LemSoundness}, plus the fact that if $\Gamma,s\ts P\from T$, then we have a commutative diagram
  \[
    \begin{tikzcd}[column sep=14.5pt]
      I \arrow[r, "\deno{s}", thick]
        & \oc S_\Gamma \arrow[r, "\cell^\Gamma", thick]
          & \oc\V_\Gamma \arrow[rr, "\mu_{\V_\Gamma}", thick, dashed] \arrow[ddd, "\deno{\Gamma\ts P}"', thick] \arrow[drr, "\runit_{\oc\V_\Gamma}" description, dotted]
            &
              & \oc\V_\Gamma \tensor \oc\V_\Gamma \arrow[rr, "\deno{\Gamma\ts P}\tensor\oc\V_\Gamma", thick, dashed] \arrow[d, "\oc\V_\Gamma\tensor()" description, dotted]
                &
                  & \deno T \tensor\oc\V_\Gamma \arrow[ddd, "{\wk_{\deno T,\oc\V_\Gamma}}" description, thick, dashed] \arrow[ddl, "\deno T \tensor ()" description, dotted] \\
      %
        &
          &
            &
              & \oc\V_\Gamma \tensor I \arrow[dr, "\deno{\Gamma\ts P}\tensor I" description, dotted] \arrow[dl, "{\wk_{\oc\V_\Gamma,I}}" description, dotted]
                &
                  & \\
      %
        &
          &
            & \oc\V_\Gamma \sequoid I \arrow[dr, "\deno{\Gamma\ts P}\sequoid I" description, dotted] \arrow[uul, "\run_{\oc\V_\Gamma}" description, dotted]
              &
                & \deno T \tensor I \arrow[dl, "{\wk_{\deno T,I}}" description, dotted]
                  & \\
      %
        &
          & \deno T
            &
              & \deno T \sequoid I \arrow[ll, "{\run_{\deno T}}"']
                &
                  & \deno T \sequoid \oc\V_\Gamma \arrow[ll, "\deno T \sequoid()"']\,,
    \end{tikzcd}
    \]
  allowing us to recover $\deno{s};\cell^\Gamma;\deno{\Gamma\ts P}$ from 
  \[
    \seqdeno{\Gamma,s\ts P} = \deno{s};\cell^\Gamma;\mu_{\V_\Gamma};(\deno{\Gamma\ts P}\tensor\oc\V_\Gamma);\wk_{\deno T,\oc\V_\Gamma}\,,
    \]
  for $P=M,c$.
\end{proof}

@@

It is then easy to see the following.
\begin{proposition}
  \begin{itemize}
    \item Given $\sigma\from A \implies B$, $\sigma;\bot_{B\implies C}=\bot_{A\implies C}$.
    \item Given a strict strategy $\tau\from B\implies C$, $\bot_{A\implies B};\tau=\bot_{A\implies C}$.
    \item Given a zigzag (copycat) strategy $\zz_\phi\from B \implies C$ and a strategy $\sigma\from A\implies B$, if $\sigma;\zz_\phi=\bot_{A\implies C}$ then $\sigma=\bot_{A\implies B}$.
  \end{itemize}
\end{proposition}

@@

\begin{definition}
  We inductively define a relation $\plot_T^\Gamma$, where $\Gamma$ is a $\Var$-store and $T$ a type, between strategies for $\oc\V_\Gamma \implies \deno T$ and terms $\Gamma\ts M\from T$ in context as follows.
  \begin{itemize}
    \item If $X\in\{\bC,\bB,\bN\}$ is a datatype, $M\from X$ and $\sigma\from \oc\V_\Gamma\implies X$, then we say that $\sigma \plot_X^\Gamma u$ if for all $\Gamma$-stores $s$, either $\seqdeno{s,\sigma}=\bot_{A\sequoid\oc\V_\Gamma}$ or $\seqdeno{s,\sigma}=\seqdeno{s',u}$ for some $\Gamma$-store $s'$ and some canonical form $u\in X$ such that $\Gamma,s\ts M \converges u,s'$.

@@

    \item If $\sigma \from \oc\V_\Gamma \implies (\oc\deno{S} \implies \deno T)$ and $M\from S \to T$, we say that $\sigma\plot_{S\to T}^\Gamma M$ if whenever $\tau\from \oc\V_\Gamma \implies \deno S$ is a strategy and $N\from S$ is a term such that $\tau\plot_S^\Gamma N$, then
      \[
        \left(\oc\V_\Gamma \xrightarrow{\mu_{\V_\Gamma}} \oc\V_\Gamma \tensor \oc\V_\Gamma \xrightarrow{\sigma\tensor\tau^\dag} (\oc\deno S \implies \deno T) \tensor \oc\deno S \xrightarrow{\ev} \deno T\right) \plot_T^\Gamma M\,N\,,
        \]
      and in addition if $S=\Var$ and $T=X$ for some datatype $X$, then
      \small
      \[
        \left(\oc\V_\Gamma \xrightarrow{\mu_{\V_\Gamma}} \oc\V_\Gamma \tensor \oc\V_\Gamma \xrightarrow{\sigma\tensor \cell} (\oc\Varr \implies X) \tensor \oc\Varr \xrightarrow{\ev} X\right) \plot_X^\Gamma \neww_X (\lambda x.M\,x)\,.
        \]
      \normalsize
  \end{itemize}
\end{definition}

\begin{lemma}
  Let $\Gamma\ts M,N\from T$ be terms in context of Idealized Algol such that
  \[
    \Gamma,s\ts M\opto \Gamma,s\ts N
    \]
  for all $\Gamma$-stores $s$.  
  Suppose $\sigma\from\oc\V_\Gamma\implies\deno T$ is a strategy such that $\sigma\plot_T^\Gamma N$.  
  Then $\sigma\plot_T^\Gamma M$.
\end{lemma}
\begin{proof}
  Induction on $T$.

@@

  Lastly, suppose that 
\end{proof}

@@

  Given a strategy $\sigma\from \oc\V_{\Gamma,\Delta}\implies \deno{T}$, we write
  \[
    (\sigma_i)\semicom \sigma
    \]
  for the composite
  \[
    \oc\V_\Gamma \xrightarrow{\langle \oc\V_\Gamma,\sigma_1^\dag,\cdots,\sigma_n^\dag\rangle} \oc\V_{\Gamma,\Delta} \xrightarrow{\sigma} \deno{T}\,.
    \]

  Then for any term-in-context $\Gamma,\Delta \ts M\from T$, we have
  \[
    (\sigma_i)\semicom\deno{\Gamma\ts M} \plot_T^{\Gamma} M[N_i/x_i]\,.
    \]
\end{lemma}

>>>>

At type $\Var$, we have terms that call the read and write `methods' to dereference the variable or to assign a new value to it.
\begin{mathpar}
  \inferrule*{\Gamma\ts V \from \Var \\ \Gamma \ts E \from \nat}{\Gamma \ts V\gets E \from \com}
  \and
  \inferrule*{\Gamma\ts V \from \Var}{\Gamma \ts \oc V \from \nat}
\end{mathpar}

@@

\begin{proposition}[\cite{SamsonGuyIAActive}]
  Suppose that $\Gamma,s\ts M\converges c,s'$.  
  Then
  \[
    \deno s;\cell^\Gamma;\deno{\Gamma\ts M} = \deno{s'};\cell^\Gamma;\deno{\Gamma\ts c}\,.
    \]
  \label{PropSoundness}
\end{proposition}
\begin{proof}
  Lemma \ref{LemSoundness}, plus the fact that if $\Gamma,s\ts P\from T$, then we have a commutative diagram
  \[
    \begin{tikzcd}[column sep=14.5pt]
      I \arrow[r, "\deno{s}", thick]
        & \oc S_\Gamma \arrow[r, "\cell^\Gamma", thick]
          & \oc\V_\Gamma \arrow[rr, "\mu_{\V_\Gamma}", thick, dashed] \arrow[ddd, "\deno{\Gamma\ts P}"', thick] \arrow[drr, "\runit_{\oc\V_\Gamma}" description, dotted]
            &
              & \oc\V_\Gamma \tensor \oc\V_\Gamma \arrow[rr, "\deno{\Gamma\ts P}\tensor\oc\V_\Gamma", thick, dashed] \arrow[d, "\oc\V_\Gamma\tensor()" description, dotted]
                &
                  & \deno T \tensor\oc\V_\Gamma \arrow[ddd, "{\wk_{\deno T,\oc\V_\Gamma}}" description, thick, dashed] \arrow[ddl, "\deno T \tensor ()" description, dotted] \\
      %
        &
          &
            &
              & \oc\V_\Gamma \tensor I \arrow[dr, "\deno{\Gamma\ts P}\tensor I" description, dotted] \arrow[dl, "{\wk_{\oc\V_\Gamma,I}}" description, dotted]
                &
                  & \\
      %
        &
          &
            & \oc\V_\Gamma \sequoid I \arrow[dr, "\deno{\Gamma\ts P}\sequoid I" description, dotted] \arrow[uul, "\run_{\oc\V_\Gamma}" description, dotted]
              &
                & \deno T \tensor I \arrow[dl, "{\wk_{\deno T,I}}" description, dotted]
                  & \\
      %
        &
          & \deno T
            &
              & \deno T \sequoid I \arrow[ll, "{\run_{\deno T}}"']
                &
                  & \deno T \sequoid \oc\V_\Gamma \arrow[ll, "\deno T \sequoid()"']\,,
    \end{tikzcd}
    \]
  allowing us to recover $\deno{s};\cell^\Gamma;\deno{\Gamma\ts P}$ from 
  \[
    \seqdeno{\Gamma,s\ts P} = \deno{s};\cell^\Gamma;\mu_{\V_\Gamma};(\deno{\Gamma\ts P}\tensor\oc\V_\Gamma);\wk_{\deno T,\oc\V_\Gamma}\,,
    \]
  for $P=M,c$.
\end{proof}

@@

It is then easy to see the following.
\begin{proposition}
  \begin{itemize}
    \item Given $\sigma\from A \implies B$, $\sigma;\bot_{B\implies C}=\bot_{A\implies C}$.
    \item Given a strict strategy $\tau\from B\implies C$, $\bot_{A\implies B};\tau=\bot_{A\implies C}$.
    \item $\bot_{A\implies B}$ is a strict strategy and $\bot_{A\implies B}\sequoid\sigma=\bot_{(A\sequoid C)\implies (B\sequoid D)}$ for any $\sigma\from C\implies D$.
    \item $\Lambda(\bot_{A\tensor B\implies C})=\bot_{A\implies(B\implies C)}$.
    \item Given a zigzag (copycat) strategy $\zz_\phi\from B \implies C$ and a strategy $\sigma\from A\implies B$, if $\sigma;\zz_\phi=\bot_{A\implies C}$ then $\sigma=\bot_{A\implies B}$.
  \end{itemize}
\end{proposition}

@@

\begin{definition}
  We inductively define a relation $\plot_T^\Gamma$, where $\Gamma$ is a $\Var$-store and $T$ a type, between strategies for $\oc\V_\Gamma \implies \deno T$ and terms $\Gamma\ts M\from T$ in context as follows.
  \begin{itemize}
    \item If $X\in\{\bC,\bB,\bN\}$ is a datatype, $M\from X$ and $\sigma\from \oc\V_\Gamma\implies X$, then we say that $\sigma \plot_X^\Gamma u$ if for all $\Gamma$-stores $s$, either $\seqdeno{s,\sigma}=\bot_{A\sequoid\oc\V_\Gamma}$ or $\seqdeno{s,\sigma}=\seqdeno{\Gamma,s'\ts u}$ for some $\Gamma$-store $s'$ and some canonical form $u\in X$ such that $\Gamma,s\ts M \converges u,s'$.

@@

    \item If $\sigma \from \oc\V_\Gamma \implies (\oc\deno{S} \implies \deno T)$ and $M\from S \to T$, we say that $\sigma\plot_{S\to T}^\Gamma M$ if whenever $\tau\from \oc\V_\Gamma \implies \deno S$ is a strategy and $N\from S$ is a term such that $\tau\plot_S^\Gamma N$, then
      \[
        \left(\oc\V_\Gamma \xrightarrow{\mu_{\V_\Gamma}} \oc\V_\Gamma \tensor \oc\V_\Gamma \xrightarrow{\sigma\tensor\tau^\dag} (\oc\deno S \implies \deno T) \tensor \oc\deno S \xrightarrow{\ev} \deno T\right) \plot_T^\Gamma M\,N\,,
        \]
      and in addition if $S=\Var$ and $T=X$ for some datatype $X$, where $M=\lambda x.M'$, then
      \begin{align*}
        \left(\oc\V_\Gamma \xrightarrow{\runit_{\oc\V_\Gamma}} \oc\V_\Gamma \tensor I \xrightarrow{\sigma\tensor (\oc 0;\cell)} (\oc\Varr \implies X) \tensor \oc\Varr \xrightarrow{\ev} X\right)\qquad\\
        \plot_X^\Gamma \neww_X M\,.
      \end{align*}
  \end{itemize}
\end{definition}

\begin{lemma}
  Let $\Gamma\ts M,N\from T$ be terms in context of Idealized Algol such that
  \[
    \Gamma,s\ts M\opto \Gamma,s\ts N
    \]
  for all $\Gamma$-stores $s$.  
  Suppose $\sigma\from\oc\V_\Gamma\implies\deno T$ is a strategy such that $\sigma\plot_T^\Gamma N$.  
  Then $\sigma\plot_T^\Gamma M$.
  \label{LemAdequacyOpto}
\end{lemma}
\begin{proof}
  Induction on $T$.

@@

  Lastly, suppose that $\Gamma,s\ts M,N\from S \to T$ and suppose that $\Gamma,s\ts M \opto \Gamma,s\ts N$.
  Let $\sigma\from \oc\V_\Gamma \implies (\oc\deno S \implies \deno T)$ be a strategy and suppose that $\sigma \plot_{S\to T} N$.  
  We claim that $\sigma \plot_{S\to T} M$.  
  Indeed, let $\tau\from\oc\V_\Gamma\implies\deno S$ be a strategy and let $\Gamma \ts P\from S$ be a term in context such that $\tau\plot_S^\Gamma P$.  
  Then, since $\sigma\plot_{S\to T} N$, we must have that $\mu_{\V_\Gamma};(\sigma\tensor\tau^\dag);\ev \plot_T^\Gamma N\,P$.  
  Since $\Gamma,s\ts M\opto\Gamma,s\ts N$, we must have $\Gamma,s\ts M\,P\opto\Gamma,s\ts N\,P$, and therefore $\mu_{\V_\Gamma};(\sigma\tensor\tau^\dag);\ev\plot_T^\Gamma M\,P$ by induction.

  In the case that $S=\Var$ and $T=X$ is a datatype, we also need to show that $\runit_{\oc\V_\Gamma};(\sigma\tensor(\oc 0;\cell));\ev\plot_X^\Gamma\neww_X(\lambda x.M\,x)$.  
  Writing $\sigma'$ for the composite $\runit_{\oc\V_\Gamma};(\sigma\tensor(\oc 0;\cell));\ev$, we know already that $\sigma'\plot_X^\Gamma \neww_X(\lambda x.N\,x)$.
  Let $s$ be a $\Gamma$-store.  
  Then we know that if $\seqdeno{s,\sigma'}\ne\bot_{\oc\V_\Gamma\implies X}$, then $\seqdeno{s,\sigma'}=\seqdeno{s',u}$ for some $s'$, $u$ such that $\Gamma,\neww_X \lambda x.N\,x\converges u,s'$.
  It follows that $\Gamma,x,(s\vert x\mapsto 0)\ts N\,x\converges u,s'$; then, since $\Gamma,x,(s\vert x\mapsto 0)\ts M\,x\opto \Gamma,x(s\vert_x\mapsto 0)\ts N\,x$, we have $\Gamma,x\ts M\,x\converges u,s'$ by Lemma \ref{LemSoundnessOpto}.
  Therefore, $\Gamma,s\ts \neww_X \lambda x.M\,x \ts u,s'$.  
  Since $s$ was arbitrary, it follows that $\sigma'\plot_X^\Gamma \new_X(\lambda x.M\,x)$.
\end{proof}

\begin{lemma}
  Let $T$ be a type of Idealized Algol, and let $\Gamma$ be a $\Var$-context.  
  Then $\bot_{\oc\V_\Gamma\implies \deno T}\plot_T^\Gamma M$ for any term-in-context $\Gamma\ts M\from T$.
  \label{LemAdequacyBot}
\end{lemma}
\begin{proof}
  Induction on $T$.  
  If $T$ is a datatype and $s$ a store, then for any $\sigma\from \oc\V_\Gamma\implies \deno T$ we have
  \[
    \oc\deno s;\cell^\Gamma;\sigma = \seqdeno{s,\sigma};(\deno T\sequoid ());\run_{\deno T}\,,
    \]
  as in the proof of Proposition \ref{PropSoundness}; since $(\deno T\sequoid());\run_{\deno T}$ is a zigzag strategy, if $\sigma=\bot_{\oc\V_\Gamma\implies\deno T}$, then $\oc\deno s;\cell^\Gamma;\sigma=\bot_{\deno T}$, and therefore $\seqdeno{s,\sigma}=\bot_{T\sequoid\oc\V_\Gamma}$.

  Suppose $\Gamma\ts M\from\Var$.  
  Since the projections are strict strategies, we have $\bot_{\oc\V_\Gamma\implies\Varr};\pr_n=\bot_{\oc\V_\Gamma\implies\bC}\plot_{\Var}^\Gamma M$ and $\bot_{\oc\V_\Gamma\implies\Varr};\pr_{\bC}=\bot_{\oc\V_\Gamma\implies\bN}\plot_{\bN}^\Gamma M$, and therefore $\bot_{\oc\V_\Gamma\implies\Varr}\plot_{\Var}^\Gamma M$.

  Suppose that $\Gamma\ts M\from S\to T$.  
  Fix some $N\from S$ and $\tau\from \oc\V_\Gamma\implies \deno S$ such that $\tau\plot_S^\Gamma N$.

  We are required to show that
  \[
    \left(\oc\V_\Gamma \xrightarrow{\mu_{\V_\Gamma}} \oc\V_\Gamma \tensor \oc\V_\Gamma \xrightarrow{\bot\tensor\tau^\dag} (\oc\deno S \implies \deno T) \tensor \oc\deno S \xrightarrow{\ev} \deno T\right) \plot_T^\Gamma M\,N\,,
    \]
  which, by induction, we can do by showing that it is equal to $\bot_{\oc\V_\Gamma\implies\deno T}$.
  Indeed, we may write this composite as
  \[
    \oc\V_\Gamma \xrightarrow{\mu_{\V_\Gamma}} \oc\V_\Gamma\tensor\oc\V_\Gamma \xrightarrow{\oc\V_\Gamma \tensor \tau^\dag} \oc\V_\Gamma\tensor\oc\deno S \xrightarrow{\Lambda\inv(\bot_{\oc\V_\Gamma \implies (\oc\deno S \implies \deno T))}} \deno T\,,
    \]
  which is equal to $\bot_{\oc\V_\Gamma\implies\deno T}$.

  Lastly, in the special case that $S=\Var$ and $T=X$ is a datatype, we need to show that
  \begin{align*}
    \left(\oc\V_\Gamma \xrightarrow{\runit_{\oc\V_\Gamma}} \oc\V_\Gamma \tensor I \xrightarrow{\sigma\tensor (\oc 0;\cell)} (\oc\Varr \implies X) \tensor \oc\Varr \xrightarrow{\ev} X\right)\qquad\\
    \plot_X^\Gamma \neww_X M\,.
  \end{align*}
  Indeed, this composite is equal to $\bot_{\oc\V_\Gamma\implies X}$ by an identical argument.
\end{proof}

\begin{lemma}
  Let $T$ be an idealized Algol type, and let $\Gamma\ts M\from T$ be a typing judgement, where $\Gamma$ is a $\Var$-context.
  Suppose that $\sigma_1\subset\sigma_2\subset\cdots$ is a nested sequence of strategies for $\oc\V_\Gamma$ such that $\sigma_i\plot_T^\Gamma M$ for all $i$.  
  Let $\sigma=\bigcup_i \sigma_i$.  
  Then $\sigma\plot_T^\Gamma M$.
  \label{LemAdequacyLimits}
\end{lemma}
\begin{proof}
  If $X$ is a datatype, $\Gamma$ is a $\Var$-context, $s$ is a $\Gamma$-store and $\Gamma\ts M\from X$ is a typing judgement, then if $\seqdeno{s,\sigma_i}=\bot_{X\sequoid\oc\V_\Gamma}$ for all $i$, then we must have $\seqdeno{s,\sigma_i}=\bot_{X\sequoid\oc\V_\Gamma} = \bot_{X\sequoid\oc\V_\Gamma}$ by continuity of composition.  
  Otherwise, $\seqdeno{s,\sigma_i}=\seqdeno{\Gamma,s'\ts u}$ for some $i$, some $\Gamma$-store $s'$ and some $u\in X$ such that $\Gamma,s\ts M \converges u,s'$.
  In that case, since $\seqdeno{\Gamma,s'\ts u}$ is a maximal strategy for $X\sequoid\oc\V_\Gamma$, we must have $\seqdeno{s,\sigma_j}=\seqdeno{\Gamma,s'\ts u}$ for all $j\ge i$, and therefore that $\seqdeno{s,\sigma}=\seqdeno{\Gamma,s'\ts u}$.

  By induction on $T$, this extends to higher types by continuity of composition.
\end{proof}

@@

  Given a strategy $\sigma\from \oc\V_{\Gamma,\Delta}\implies \deno{T}$, we write
  \[
    (\sigma_i)\semicom \sigma
    \]
  for the composite
  \[
    \oc\V_\Gamma \xrightarrow{\langle \der,\sigma_1,\cdots,\sigma_n^\dag\rangle^\dag} \oc\V_{\Gamma,\Delta} \xrightarrow{\sigma} \deno{T}\,.
    \]

  Then for any term-in-context $\Gamma,\Delta \ts M\from T$, we have
  \[
    (\sigma_i)\semicom\deno{\Gamma,\Delta\ts M} \plot_T^{\Gamma} M[N_i/x_i]\,.
    \]
  \label{LemAdequacy}
\end{lemma}
\begin{proof}
  Induction on the typing derivation $\Gamma,\Delta \ts M\from T$.

  \begin{itemize}
    \item Let $x_j\from T_j$ be a variable occurring in $\Delta$.  
      Then $x_j[N_i/x_i]=N_j$.  
      Moreover, it is clear that $(\sigma_i)\semicom \deno{\Gamma,\Delta\ts x_j} = \sigma_j$.
      And we have $\sigma_j\plot_{T_j}^\Gamma N_j$ by hypothesis.

    \item Next, suppose that $x\from\Var$ is a variable occurring in $\Gamma$.
      Then we have $x[N_i/x_i]=x$, and it is easy to see that we have
      \[
        (\sigma_i)\semicom\deno{\Gamma,\Delta\ts x} = \deno{\Gamma\ts x}\,.
        \]
      Now we have $\deno{\Gamma\ts x};\pr_n = \deno{\Gamma\ts x\gets n}$ and $\deno{\Gamma\ts x};\pr_{\bN} = \deno{\Gamma \ts \oc\bN}$.  
      From Lemma \ref{LemSoundnessOpto} (in particular, Figures \ref{FigSoundnessOoptoContext} and \ref{FigSoundnessOoptoStorage}), we know that if $s$ is a $\Gamma$-store, then
      \[
        \seqdeno{s,\deno{\Gamma\ts x\gets n}} = \seqdeno{\Gamma,s\ts x\gets n} = \seqdeno{\Gamma, (s\vert x\mapsto n)\ts \skipp}\,,
        \]
      where we have that $\Gamma,s\ts x\gets n\converges \skipp,(s\vert x\mapsto n)$, and that
      \[
        \seqdeno{s,\deno{\Gamma\ts \oc x}} = \seqdeno{\Gamma,s\ts \oc x} = \seqdeno{\Gamma,s\ts s(x)}\,,
        \]
      where we have that $\Gamma,s\ts \oc x \converges s(x),s$.

    \item Next, suppose that $\Gamma,\Delta\ts M\from S\to T$ and $\Gamma,\Delta\ts N\from S$, where we already know that
      \[
        (\sigma_i)\semicom\deno{\Gamma,\Delta\ts M}\plot_{S\to T}^\Gamma M[N_i/x_i]
        \]
      and that
      \[
        (\sigma_i)\semicom\deno{\Gamma,\Delta\ts N}\plot_S^\Gamma N[N_i/x_i]\,.
        \]
      Then it easy to see that
      \[
        (\sigma_i)\semicom\deno{\Gamma,\Delta\ts M\,N}
        \]
      is given by the composite
      \small
      \[
        \oc\V_\Gamma \xrightarrow{\mu_{\V_\Gamma}} \oc\V_\Gamma \tensor \oc\V_\Gamma \xrightarrow{((\sigma_i)\semicom\deno{\Gamma,\Delta\ts M}) \tensor ((\sigma_i)\semicom\deno{\Gamma,\Delta\ts N})} (\oc\deno S \implies \deno T) \tensor \oc\deno {S} \xrightarrow{\ev} \deno T.
        \]
      \normalsize
      Therefore, by the definition of $\plot_{S\to T}^\Gamma$, it must be the case that
      \[
        (\sigma_i)\semicom\deno{\Gamma,\Delta\ts M\,N} \plot_{T}^\Gamma M[N_i/x_i]\,N[N_i/x_i] = (M\,N)[N_i/x_i],.
        \]
    \item Next, suppose that $\Gamma,\Delta,x\from S \ts M\from T$.  
      We claim that
      \[
        (\sigma_i)\semicom\deno{\Gamma,\Delta,\lambda x.M} \plot_{S\to T}^\Gamma (\lambda x.M)[N_i/x_i]\,.
        \]
      Let $\sigma'\from \oc\V_\Gamma \implies \deno S$ be a strategy and let $\Gamma\ts N\from S$ be a term in context such that $\sigma\plot_S^\Gamma N$.  
      Then, by the inductive hypothesis (with $x$ lying in the `$\Delta$-part', we know that
      \[
        (\sigma_i,\sigma')\semicom\deno{\Gamma,\Delta,x\from S\ts M\from T}\plot_T^\Gamma M[N_i/x_i,N'/x]\,.
        \]
      Then, since $\Gamma,s\ts (\lambda x.M[N_i/x_i])\,N'\opto \Gamma,s\ts M[N_i/x_i,N'/x]$ for any $\Gamma$-store $s$, by Lemma \ref{LemAdequacyOpto} we know that
      \[
        (\sigma_i,\sigma')\semicom\deno{\Gamma,\Delta,x\from S\ts M} \plot_T^\Gamma ((\lambda x.M)[N_i/x_i])\,N'\,.
        \]
      Finally, observe that $(\sigma_i,\sigma')\semicom\deno{\Gamma,\Delta,x\from S\ts M\from T}$ is the composite
      \[
        \oc\V_\Gamma \xrightarrow{\langle\der,\sigma_1,\cdots,\sigma_n,\sigma'\rangle^\dag} \oc\V_{\Gamma,\Delta,x} \xrightarrow{\deno{\Gamma,\Delta,x\from S\ts M}} \deno T\,,
        \]
      which can alternatively be written as
      \begin{mathpar}
        \oc\V_\Gamma \xrightarrow{\langle\der,\sigma_1,\cdots,\sigma_n\rangle^\dag} \oc\V_{\Gamma,\Delta} \xrightarrow{\mu_{\V_{\Gamma,\Delta}}} \oc\V_{\Gamma,\Delta}\tensor\oc\V_{\Gamma,\Delta}\\ \xrightarrow{\deno{\Gamma,\Delta\ts \lambda x.M} \tensor (\sigma')^\dag} (\oc\deno S\implies \deno T) \tensor \oc\deno S \xrightarrow{\ev} \deno T\,.
      \end{mathpar}

      In the special case that $S=\Var$ and $T=X$ is a datatype, we need to show that we also have
      \begin{mathpar}
        \bigg(\oc\V_\Gamma \xrightarrow{\langle\der,\sigma_1,\cdots,\sigma_n\rangle^\dag}
        \oc\V_{\Gamma,\Delta} \xrightarrow{\runit_{\oc\V_{\Gamma,\Delta}}}
        \oc\V_{\Gamma,\Delta}\tensor I \xrightarrow{\oc\V_{\Gamma,\Delta} \tensor \oc0}
        \oc\V_{\Gamma,\Delta}\tensor\oc\bN \xrightarrow{\oc\V_{\Gamma,\Delta}\tensor\cell}
        \oc\V_{\Gamma,\Delta}\tensor\oc\Var \xrightarrow{\deno{\Gamma,\Delta\ts\lambda x.M}\tensor \oc\Var}\\
        (\oc\Var \implies X) \tensor \oc\Var \xrightarrow{\ev}
        X\bigg)
        \plot_X^\Gamma \neww_X \lambda x.M[N_i/x_i]\,.
      \end{mathpar}
      Call this composite (in brackets) $\zeta$.

      By induction (taking $x$ to be in the `$\Gamma$-component'), we know already that
      \begin{mathpar}
        \left(
        \oc\V_{\Gamma,x} \xrightarrow{\langle\pr_\Gamma,\sigma_1,\cdots,\sigma_n,\pr_x\rangle^\dag}
        \oc\V_{\Gamma,\Delta,x} \xrightarrow{\deno{\Gamma,\Delta,x\ts M}}
        X
        \right)
        \plot_X^{\Gamma,x} M[N_i/x_i]\,.
      \end{mathpar}
      Call this composite $\xi$.  
      Then we can write the first composite $\zeta$ as
      \begin{mathpar}
        \oc\V_\Gamma \xrightarrow{\langle\der,\sigma_1,\cdots,\sigma_n\rangle^\dag}
        \oc\V_{\Gamma,\Delta} \xrightarrow{\runit_{\oc\V_{\Gamma,\Delta}}}
        \oc\V_{\Gamma,\Delta}\tensor I \xrightarrow{\oc\V_{\Gamma,\Delta} \tensor \oc0}
        \oc\V_{\Gamma,\Delta}\tensor\oc\bN \xrightarrow{\oc\V_{\Gamma,\Delta}\tensor\cell}
        \oc\V_{\Gamma,\Delta}\tensor\oc\Var \xrightarrow{\xi}
        X\,.
      \end{mathpar}
      Therefore, for any $\Gamma$-store $s$, either $\seqdeno{s,\xi}=\bot$, in which case $\seqdeno{s,\zeta}=\bot$, or $\seqdeno{(s\vert x\mapsto 0),\xi}=\seqdeno{s',u}$ for some $u$ in $X$ and some $\Gamma,x$-store $s'$ such that $\Gamma,x,(s\vert x\mapsto 0) \ts M \converges u,s'$.  
      In the second case, we have $\seqdeno{s,\zeta} = \seqdeno{s'\vert_\Gamma,u}$, and $\Gamma,s\ts M \converges u,s'\vert_\Gamma$.
  \end{itemize}

  Now we move on to the structural constants for the datatypes.  
  We deal with the case of the type $\nat$ (i.e., the terms $n$, $\suc M$, $\pred M$ and $\IfO M\Then N \Else P$, and it should be clear how our ideas translate to the corresponding rules at the types $\com$ and $\bool$.

  \begin{itemize}
    \item Given a numeral $n$ and a $\Gamma$-store $s$, we have $(\sigma_i)\semicom \deno{\Gamma,\Delta\ts n} = \deno{\Gamma\ts n}$ and $\seqdeno{s,\deno{\Gamma\ts n}} = \seqdeno{\Gamma,s\ts n}$, where $\Gamma,s\ts n\converges n,s$.

    \item Suppose $\Gamma,\Delta\ts M\from \nat$, and that we already know that 
      \[
        (\sigma_i)\semicom\deno{\Gamma,\Delta\ts M}\plot_{\nat}^\Gamma M[N_i/x_i]\,.
        \]
      So for all $\Gamma$-stores $s$, either $\seqdeno{s,((\sigma_i)\semicom\deno{\Gamma,\Delta\ts M})} = \bot_{\bN\sequoid\oc\V_\Gamma}$ or it is equal to $\seqdeno{\Gamma,s'\ts n}$ for some numeral $n$.

      Now we have 
      \[
        (\sigma_i)\semicom\deno{\Gamma,\Delta\ts\suc M} = (\sigma_i)\semicom\deno{\Gamma,\Delta\ts M};(\suc\tensor\oc\V_\Gamma)\,;
        \]
      since $\suc\from\bN \implies \bN$ is a strict strategy, we know that either $\seqdeno{s,((\sigma_i)\semicom\deno{\Gamma,\Delta\ts \suc M})} = \bot_{\bN\sequoid\oc\V_\Gamma}$ or it is equal to $\seqdeno{\Gamma,s'\ts n};(\suc\tensor\oc\V_\Gamma) = \seqdeno{\Gamma,s'\ts n+1}$, and we have $\Gamma,s\ts \suc M[N_i/x_i]\converges n+1$.
      Therefore, 
      \[
        (\sigma_i)\semicom\deno{\Gamma,\Delta\ts\suc M} \plot_{\nat}^\Gamma \suc M[N_o/x_i]\,.
        \]

      A similar argument proves that 
      \[
        (\sigma_i)\semicom\deno{\Gamma,\Delta\ts\pred M} \plot_{\nat}^\Gamma \pred M[N_i/x_i]\,.
        \]
